`phyr`: An R package for phylogenetic species-distribution modelling in ecological communities

### 2020-02-14 ms.Rmd
Aligning equations by ~ or =

$$y=(\beta_{0}+b_{0\_sp}+b_{0\_site})+(\beta_{1}+b_{1})envi+(\beta_{2}+b_{2})trait+\beta_{3}envi*trait+b_{3}+e$$
$$b_{0\_{sp}}\sim Gaussian(0,\sigma_{0\_{sp}}^{2}\Sigma_{spp})$$
$$b_{0\_{site}}\sim Gaussian(0,\sigma_{0\_{site}}^{2}\Sigma_{site})$$
$$b_{1}\sim Gaussian(0,\sigma_{1}^{2}\Sigma_{spp})$$
$$b_{2}\sim Gaussian(0,\sigma_{2}^{2}I_{site})$$
$$b_{3}\sim Gaussian(0,\sigma_{3}^{2}\Sigma_{site}\otimes\Sigma_{spp})$$
$$e\sim Gaussian(0,\sigma_{e}^2)$$

>>>>

\begin{align*}
y = & ~ (\beta_{0}+b_{0\_sp}+b_{0\_site})+(\beta_{1}+b_{1})envi+(\beta_{2}+b_{2})trait+\beta_{3}envi*trait+b_{3}+e \\
b_{0\_{sp}} \sim & ~ \text{Gaussian}(0,\sigma_{0\_{sp}}^{2}\Sigma_{spp}) \\
b_{0\_{site}} \sim & ~ \text{Gaussian}(0,\sigma_{0\_{site}}^{2}\Sigma_{site}) \\
b_{1} \sim & ~ \text{Gaussian}(0,\sigma_{1}^{2}\Sigma_{spp}) \\
b_{2} \sim & ~ \text{Gaussian}(0,\sigma_{2}^{2}I_{site}) \\
b_{3} \sim & ~ \text{Gaussian}(0,\sigma_{3}^{2}\Sigma_{site}\otimes\Sigma_{spp}) \\
e \sim & ~ \text{Gaussian}(0,\sigma_{e}^2)
\end{align*}
